---
title: 'AAEC 4984/5484: Applied Economic Forecasting'
author: "Put your name here"
date: |
    Homework #2 - Spring `r format(Sys.Date(),"%Y")` 
output: 
  pdf_document:
    keep_tex: no

header-includes:
 \usepackage{float} #fixes position of figures
geometry: margin=0.8in # sets the page margins
---

```{r setup, include=FALSE}
library(fpp2)
theme_set(theme_bw()) # change if you would like.
knitr::opts_chunk$set(echo = TRUE, fig.pos = 'H')
```


The purpose of this assignment is to enhance your understanding of time series and data patterns. It is intended to be rather straightforward and simple.

**Instructions**: 

- **Where necessary, please ensure that your graphs and visuals have properly titles and axes labels.** 
- Recall that you can use `help()` to find out about the data in each series. 

# Question 1: Visualizing Time Series Data

Create time plots of the following time series: `bicoal`, `chicken`, `dole`, `usdeaths`, `lynx`, `goog`, `writing`, `fancy`, `a10`, `h02`. 

- Please use the `grid.arrange` function of the `gridExtra` package to arrange your plots as a `5 x 2` grid. Below, I have provided the base code to achieve this. 


```{r Q1plots, eval = FALSE, fig.height=9.5,out.width="\\textwidth"} 
# To display your graphs, remember to delete the eval = FALSE code chunk option. 
# Edit the height etc to match your preference.
g1 <- autoplot(.) + labs(title = ".", x ="" , y = "  ")
g2 <- "..." 
g3 <- "..."
g4 <- "..."
g5 <- "..."
g6 <- "..."
g7 <- "..."
g8 <- "..."
g9 <- "..."
g10 <- "..."

gridExtra::grid.arrange(......, nrow=5,ncol=2)
```

\newpage

# Question 2: Assessing Seasonality

i. Use the `ggseasonplot()`, `ggsubseriesplot()`, and `ggAcf` functions to explore possible seasonality in the following time series: `writing`, `fancy`, `a10`, `h02`. 

- Please use the `grid.arrange` function of the `gridExtra` package to arrange your plots. You are free to organize them by chart type or series.

- **It might be useful to set the max lag in the ACF to 36 so that you can see a fair bit of the patterns in the correlogram.** 

ii. What can you say about the seasonal patterns?

iii. Can you identify any unusual years?

\newpage

# Question 3: White Noise?

`goog` contains closing stock prices of Google Inc., now Alphabet Inc. (GOOG), from the NASDAQ exchange, for 1000 consecutive trading days between 25 February 2013 and 13 February 2017. 

i. Plot this series and its ACF. Comment on any pattern noticed in both. Does this series look like white noise?

ii. Now, use `dgoog <- diff(goog)` to compute the daily changes in the index. 

iii. Produce an `autoplot` of `dgoog` and its `ggAcf`. Do the changes in the Daily Google Stock prices look like white noise?**Recall that a simple yes will not suffice. You will need to explain your conclusion.**


