---
title: 'AAEC 4984/5484: Applied Economic Forecasting'
author: "Your Name Here"
date: |
    Homework #3 - Spring `r format(Sys.Date(),"%Y")` 
output: pdf_document
header-includes:
 \usepackage{float}
geometry: margin=0.8in
---

```{r setup, include=FALSE}
library(fpp2)
knitr::opts_chunk$set(echo = TRUE, fig.pos = 'H', fig.height = 3, out.width="\\textwidth") 
theme_set(theme_bw()) #Feel free to change if you like
```

**Instructions**: In all cases, please ensure that your graphs and visuals have properly titles and axes labels, where necessary. Refer to the output, whenever appropriate, when discussing the results. **Lastly, remember that creativity (coupled with relevance) will be rewarded.**

# US Natural Gas Consumption

The purpose of this exercise is two fold. On the one hand, we are using pulling real world data from a web source directly into `R`. Specifically, data on monthly U.S. Natural Gas Total Consumption is collected directly from the U.S. Energy Information Administration (EIA)-- <https://www.eia.gov/dnav/ng/hist/n9140us2m.htm>. 

On the other, we aim to **estimate** and **evaluate** the performance of our basic forecasting model in-sample (training period) and out-of-sample (testing period). Throughout, we will be build on the previous lectures and homework.

At the end, you will select an "optimal" model for modeling the future value of consumption.

**Note: Before you proceed, please install the `readxl` package. Be sure to do this in your *console* and not within the .Rmd file.**

1. Using my code below, import the NG consumption data from the EIA into `R`.

```{r importdata}
# Store file to your computer's temporary memory
tmp <- tempfile(fileext = ".xls") 
# Downlaoding data from EIA and store in tmp
download.file(url = "https://www.eia.gov/dnav/ng/hist_xls/N9140US2m.xls", 
              destfile = tmp, mode="wb")
```

2. Next, using the `read_excel()` function from the `readxl` package you were instructed to install earlier, we will read in the temporary file, `tmp`, into `R`. 

We will need to skip the first 2 rows using `skip = 2`, since they are not our column headings. Also, we will need to set `sheet = 2` since our data appears on the second worksheet.

**Feel free to manually download the excel file from the EIA link above and explore this on your own.** 

**Task: Your task will be to store this as `ngdata`.**

```{r readdata}
_____ <- readxl::read_excel(tmp, sheet = ____, skip = ____)
```

3. Extract the second column of `ngdata` ("U.S. Natural Gas Total Consumption (MMcf)") and declare it as time series object starting at January 2001. **Be sure to specify the proper frequency**. 

- Save this as `tsng`.

```{r tsng}
____ <- ____(ngdata[,____],start = ____, frequency = ____)
```

4. Present a `autoplot` of `tsng`. Briefly comment on your plot.
**Be sure to properly label your axes**.


5.  Besides the graph above, using **at least 3 graphs** you have learned so far,

- **comment** on possible seasonality and/or trends in the consumption data. 

- Would you say that the series appears to be white noise? 
**Remember that a simple yes will not suffice!**

- **Use the `gridExtra` package to create a 3 x 1 grid as in HW2.**


6. Let's proceed to forecast the `tsng` series. It would be useful to split the data set into a training (`train.ng`) and testing set period (`test.ng`). 

Assign the last **4 years** of data (November 2017 -- November 2021) to the testing period, `test.ng`. The remainder will be assigned to `train.ng`.


7. Confirm that the data is properly split by using the `autoplot` and `autolayer` function. Be sure to include `tsng`, `train.ng` and `test.ng` in this plot. *A title is not necessary.* 

**If your data is properly subsetted then the training and test series should span the entire sample period in `tsng`. 
\underline{You can ignore a small line segment that connects the training and testing datasets.}**


8. Given your conclusion earlier regarding seasonality and trends, use the appropriate benchmark models from class to forecast the **training set**. 

- **Use a horizon of 4 years. That is h = 48.**
- In this step, you are only required to store your forecasts.

**Note: If you concluded that there was no trend, I would not expect to see the `drift` method as a potential model here, for example. *Spoiler: There should be no clear trend from the ACF.* **


9. Following your class notes, `cbind` your data series, `tsng`, and point forecasts (extracting the mean columns) of your 3 forecast models and store into a variable called `tmp`. Next, produce a single graph of the elements of `tmp`.

Your aim here is to visualize the model fits for each method against the test data. We will perform formal testing later. 


10. Briefly, comment on your observations from your graph in Part 9.


11. Using the `accuracy` command, compare the fitted values of the training period against the test set.
  - Extract the `RMSE`, `MAE`, `MAPE`, and `MASE` statistics.
  - Remember to keep only the `Test set` row (Row 2)
  - Display your results as a table using the `knitr::kable( )` function with `digits = 3`.   
    - Be sure to have appropriate column and row labels.
  - Which model is preferred under the each of the 4 selection criteria?
  
**It would help to modify the codes presented in the class notes.**
  

12. Using the `checkresiduals` command, comment on the residuals from the model preferred by the `MAPE`. In particular, 
    - Do they appear to be normally distributed?
    - From the ACF and Ljung-Box test, does there appear to correlation among the residuals? **Be sure to state the null of the Ljung-Box test and how you arrive at your conclusion.**


